Self-tunable approximated explicit MPC: Heat exchanger implementation and analysys

### 2023-02-02 paper/elsarticle/main.tex
one update in nomenclature

	\subsection*{Symbols}
%	\begin{center}
		\begin{tabular}{ l l }
			$A$ & system state matrix \\
			$\widetilde{A}$ & augmented system state matrix \\
			$B$ & system input matrix \\
			$\widetilde{B}$ & augmented system input matrix \\
			$C$ & system output matrix \\
			$\widetilde{C}$ & augmented system output matrix \\
			$d_{\max}$ & maximal deviation from the steady-state value \\
			$F$ & slope of the affine control law \\
			$g$ & section of the affine control law \\
			$I$ & identity matrix \\
			$k$ & step of the prediction horizon \\
			$N$ & prediction horizon \\
			$n_{\mathrm{u}}$ & size of system inputs \\
			$n_{\mathrm{y}}$ & size of system outputs \\
			$n_{\widetilde{\mathrm{x}}}$ & size of augmented system states \\
			$Q_{\mathrm{x}}$ & penalty matrix of the built-in integrator \\
			$Q_{\mathrm{x,L}}$ & lower bound on the penalty matrix of the built-in integrator \\
			$Q_{\mathrm{x,U}}$ & upper bound on the penalty matrix of the built-in integrator \\
			$Q_{\mathrm{y}}$ & penalty matrix of the control error \\
			$Q_{\mathrm{y,L}}$ & lower bound on the penalty matrix of the control error \\
			$Q_{\mathrm{y,U}}$ & upper bound on the penalty matrix of the control error \\
			$R$ & penalty matrix of system inputs \\
			$R_{\mathrm{L}}$ & lower bound on the penalty matrix of system inputs \\
			$R_{\mathrm{U}}$ & upper bound on the penalty matrix of system inputs \\
			$\mathcal{R}$ & critical region \\
			$\mathbb{R}$ & Euclidean space of real numbers \\
			$t$ & time, s \\
			$t_{\epsilon}$ & settling time, s \\
			$T$ & temperature, $^{\circ}\mathrm{C}$ \\
			$T_{\mathrm{ref}}$ & reference temperature, $^{\circ}\mathrm{C}$ \\
			$T_{\mathrm{s}}$ & sampling time, s \\
			$T^{\mathrm{s}}$ & steady state of temperature, $^{\circ}\mathrm{C}$ \\
			$u$ & control inputs \\
		\end{tabular}
%	\end{center}

>>>>

	\subsection*{Symbols}
%	\begin{center}
		\begin{tabular}{ l l }
			$A$ & system state matrix \\
			$\widetilde{A}$ & augmented system state matrix \\
			$B$ & system input matrix \\
			$\widetilde{B}$ & augmented system input matrix \\
			$C$ & system output matrix \\
			$\widetilde{C}$ & augmented system output matrix \\
			$d_{\max}$ & maximal deviation from the steady-state value \\
			$F$ & slope of the affine control law \\
			$g$ & section of the affine control law \\
			$I$ & identity matrix \\
			$k$ & step of the prediction horizon \\
			$N$ & prediction horizon \\
			$n_{\mathrm{u}}$ & size of system inputs \\
			$n_{\mathrm{y}}$ & size of system outputs \\
			$n_{\widetilde{\mathrm{x}}}$ & size of augmented system states \\
			$P$ & proportional gain of proportional controller\\
			$Q_{\mathrm{x}}$ & penalty matrix of the built-in integrator \\
			$Q_{\mathrm{x,L}}$ & lower bound on the penalty matrix of the built-in integrator \\
			$Q_{\mathrm{x,U}}$ & upper bound on the penalty matrix of the built-in integrator \\
			$Q_{\mathrm{y}}$ & penalty matrix of the control error \\
			$Q_{\mathrm{y,L}}$ & lower bound on the penalty matrix of the control error \\
			$Q_{\mathrm{y,U}}$ & upper bound on the penalty matrix of the control error \\
			$R$ & penalty matrix of system inputs \\
			$R_{\mathrm{L}}$ & lower bound on the penalty matrix of system inputs \\
			$R_{\mathrm{U}}$ & upper bound on the penalty matrix of system inputs \\
			$\mathcal{R}$ & critical region \\
			$\mathbb{R}$ & Euclidean space of real numbers \\
			$t$ & time, s \\
			$t_{\epsilon}$ & settling time, s \\
			$T$ & temperature, $^{\circ}\mathrm{C}$ \\
			$T_{\mathrm{ref}}$ & reference temperature, $^{\circ}\mathrm{C}$ \\
			$T_{\mathrm{s}}$ & sampling time, s \\
			$T^{\mathrm{s}}$ & steady state of temperature, $^{\circ}\mathrm{C}$ \\
			$u$ & control inputs \\
		\end{tabular}
%	\end{center}
